### 2024-07-27 conteudo/tool/architecture.tex
add transformation fig

\begin{figure}
\includegraphics{diagrama_mestrado}
\caption{The architecture diagram demonstrating the relationship between the tool components.}
\label{fig:diagram}
\end{figure}

@@

The Function Parser receives the input codebase and transforms it into the temporary codebase. The 
Function Parser iterates through every source code file from the programming language it supports 
and uses a specific programming language function extractor to extract every function in the file. 
For each function extracted, we create two new source code files and a metadata file in the temporary 
codebase, represented by the pair \textbf{<file name, function name>},  the source code file of the function, and the proper function. 
The first new source code file contains the function’s body from the function it represents, while 
the other new source code file contains the function’s signature. The metadata file contains 
additional relevant information about the function, such as the function name, the line where the 
function signature starts in the source code file, and the line where the function’s body ends in 
the source code file. The programming language we support at the moment is C and Java. Can be found 
an example of a transformation of a source code in Figure (CREATE FIGURE AND ADD HERE).

@@

The temporary codebase is a transformation of the input codebase done by the Function Parser. 
Each function in the input codebase is represented in the temporary codebase as three files.
Descriptions of these files are provided below, and an example of each can be found in 
the figure (CREATE FIGURE AND ADD HERE).

>>>>

\begin{figure}
\includegraphics{diagrama_mestrado}
\caption{Architecture diagram demonstrating the relationship between the tool components.}
\label{fig:diagram}
\end{figure}

@@

The Function Parser receives the input codebase and transforms it into the temporary codebase. The 
Function Parser iterates through every source code file from the programming language it supports 
and uses a specific programming language function extractor to extract every function in the file. 
For each function extracted, we create two new source code files and a metadata file in the temporary 
codebase, represented by the pair \textbf{<file name, function name>},  the source code file of the function, and the proper function. 
The first new source code file contains the function’s body from the function it represents, while 
the other new source code file contains the function’s signature. The metadata file contains 
additional relevant information about the function, such as the function name, the line where the 
function signature starts in the source code file, and the line where the function’s body ends in 
the source code file. The programming language we support at the moment is C and Java. 
Figure \ref{fig:transform} illustrates an example of a function transformation into the 
temporary codebase.

\begin{figure}
\includegraphics[scale=0.3]{example_function_parser/example_parser}
\caption{Transformation of a function into the temporary codebase}
\label{fig:transform}
\end{figure}

@@

The temporary codebase is a transformation of the input codebase done by the Function Parser. 
Each function in the input codebase is represented in the temporary codebase as three files.
Descriptions of these files are provided below, and an example of each can be found in 
the figure \ref{fig:transform}.
